Osmia lignaria larval development response to heatwave treatments

https://doi.org/10.5061/dryad.kkwh70sb7

Authors: Grace G. Melone, Clara Stuligross, and Neal M. Williams. University of California, Davis

Description of the data and file structure

See methodology in associated manuscript. 

NestNumber: individual nest which contained multiple bees

BeeID: individually marked bee 

Treatment: integer value 1-5 indicating heatwave treatment: 

Control

Low temperature, Short duration

Low temperature, Long duration

High temperature, Short duration

High temperature, Long duration 

DurationX: integer value 4 or 7, indicating short or long heatwave duration 

TemperatureX: integer value 25, 33, or 37, indicating control, low temperature heatwave, and high temperature heatwave temperatures, respectively. While temperature is marked as 33 in the data, the true temperature as indicated by temperature loggers in incubators was 31. 

DateCollected: Month/Day corresponding to the date completed nests were collected for the experiment 

Location: character value of NH or SH, corresponding to which hoop house nests were collected from

Position: integer value indicating position in nest, where 1 was the first egg at the end of the nest bees would start from. 

EstimatedSex: integer value of 0 or 1 indicating estimated sex, with 0 indicating males and 1 indicating females. 

StageOnCollection: larval stage bees were in when nests were collected (0 as all bees used were in the egg stage)

Instar1: integer value indicating the number of days from collection to develop to instar 1

Instar2: integer value indicating the number of days from collection to develop to instar 2

Instar34: integer value indicating the number of days from collection to develop to instar 3 or 4.

Instar5: integer value indicating the number of days from collection to develop to instar 5.

SpinStart: integer value indicating the number of days from collection to begin spinning cocoons.

CocoonComplete: integer value indicating the number of days from collection to completing spinning of the cocoon.

Mortality: integer value of 0 or 1, with 0 indicating bees survived and 1 indicating bees died before reaching the end of prepupal development.

MortalityDate: month/day indicating the date bees died. 

DaystoDeath: integer value indicating the number of days from collection to mortality

DeathStage: integer corresponding to larval stage at which bees died: 

       0 .  egg stage

instar 1

instar 2

instar 3

instar 4

instar 5

Weight: fresh integer indicating fresh weight of bees in grams which completed cocoons, all bees were weighed in early July 2020

Weight_Sept: integer indicating fresh weight of bees in grams  which completed cocoons in September of 2020

Weight_Nov: integer indicating fresh weight of bees in grams which completed cocoons in November of 2020

Notes: notes taken throughout the experiment 

Sharing/Access information

This is a section for linking to other ways to access the data, and for linking to sources the data is derived from, if any.

Links to other publicly accessible locations of the data:

http://...

Code/Software

This is an optional, freeform section for describing any code in your submission and the software used to run it.

Describe any scripts, code, or notebooks (e.g., R, Python, Mathematica, MatLab) as well as the software versions (including loaded packages) that you used to run those files. If your repository contains more than one file whose relationship to other scripts is not obvious, provide information about the workflow that you used to run those scripts and notebooks.